Relationship between solar wind, $D_{st}$, and plasmasphere trough mass density on one-hour time scales

### 2016-05-12 paper/paper.tex

\begin{figure}[htp!]
\centering
\includegraphics[scale=0.45]{paperfigures/alldata-GOES6-1983-1991.eps}
\caption{Overview of data used in this article. The top four panels show parameters from \cite{Kondrashov2014ReconstructionOfGaps} and the bottom panel contains $\rho_{eq}$ based on GOES 6 measurements from \cite{Denton} after interpolation and averaging described in the text. Dashed horizontal lines in the $D_{st}$ and $\rho_{eq}$ panels indicate sample event cutoff thresholds of $D_{st} = -50$~nT and $\rho_{eq} = 20$~amu/cm$^3$} considered in Section~3.
\label{AllData}
\end{figure}

\begin{figure}[htp!]
\centering
\includegraphics[scale=0.40]{paperfigures/F107MD27d-GOES6.eps}
\includegraphics[scale=0.40]{paperfigures/ccplot-GOES6.eps}
\caption{Top: 27-day non-overlapping medians of $F_{10.7}$ and $\log(\rho_{eq})$ from GOES 6. Bottom: Correlation between $\log(\rho_{eq})$ and $F_{10.7}$ using medians in non-overlapping hour, day, and 27-day windows.}
\label{ccplot}
\end{figure}
\clearpage

\begin{figure}[tp!]
\centering
\includegraphics[scale=0.40]{paperfigures/stormavs-dst-50-tak-GOES6.eps}
\rule[1ex]{5cm}{1pt}
\includegraphics[scale=0.40]{paperfigures/stormavs-dst-day-GOES6.eps}
\caption{$D_{st}$ events from GOES 6 using daily medians. Top: Events in the interval 1989-1991; compare to \cite{Takahashi2010} Fig.~11. Bottom: Events in the interval 1983-1991.}
\label{DailyAveragedDstEvents}
\end{figure}

\begin{figure}[tp!]
\centering
\includegraphics[scale=0.40]{paperfigures/stormavs-dst.eps}
\rule[1ex]{5cm}{1pt}
\includegraphics[scale=0.40]{paperfigures/stormavs-dd12-GOES6.eps}
\caption{$D_{st}$ events from GOES 6 using hourly medians. Top: Events in the interval 1983-1991; compare to bottom panel {DailyAveragedDstEvents}. Bottom: Same as Top except for constraint that $D_{st}$ stayed below $-50$~nT for at least 12~hours after crossing below $-50$~nT.}
\label{HourlyAveragedDstEvents}
\end{figure}

@@

\begin{figure}[htp!]
\centering
\includegraphics[scale=0.40]{paperfigures/stormavs-mass-gt20-GOES6.eps}
\caption{$\req\ > 20$~ amu/cm$^3$ events from GOES 6 using hourly medians. As described in the text, there is no statistically significant dependence of the \req\  plot on $B_z$ in the time interval of $\pm 2$~hours around the event.}
\label{HourlyAveragedRhoEvents}
\end{figure}

\begin{figure}[tp!]
	\centering
	\includegraphics[scale=0.40]{paperfigures/RhoBinnedBz-case24-t020-tf25-GOES6.eps}
	\includegraphics[scale=0.40]{paperfigures/RhoBinnedBz-case24-t025-tf30-GOES6.eps}
	\caption{Binning \req\ events by $B_z$ value (a) at onset and four hours before, and (b) at onset and four hours after.}
	\label{fig:RhoBinned}
\end{figure}

>>>>

\begin{figure}[htp!]
\centering
\includegraphics[scale=0.45]{figures/alldata-GOES6-1983-1991.eps}
\caption{Overview of data used in this article. The top four panels show parameters from \cite{Kondrashov2014ReconstructionOfGaps} and the bottom panel contains $\rho_{eq}$ based on GOES 6 measurements from \cite{Denton} after interpolation and averaging described in the text. Dashed horizontal lines in the $D_{st}$ and $\rho_{eq}$ panels indicate sample event cutoff thresholds of $D_{st} = -50$~nT and $\rho_{eq} = 20$~amu/cm$^3$} considered in Section~3.
\label{AllData}
\end{figure}

\begin{figure}[htp!]
\centering
\includegraphics[scale=0.40]{figures/F107MD27d-GOES6.eps}
\includegraphics[scale=0.40]{figures/ccplot-GOES6.eps}
\caption{Top: 27-day non-overlapping medians of $F_{10.7}$ and $\log(\rho_{eq})$ from GOES 6. Bottom: Correlation between $\log(\rho_{eq})$ and $F_{10.7}$ using medians in non-overlapping hour, day, and 27-day windows.}
\label{ccplot}
\end{figure}
\clearpage

\begin{figure}[tp!]
\centering
\includegraphics[scale=0.40]{figures/stormavs-dst-50-tak-GOES6.eps}
\rule[1ex]{5cm}{1pt}
\includegraphics[scale=0.40]{figures/stormavs-dst-day-GOES6.eps}
\caption{$D_{st}$ events from GOES 6 using daily medians. Top: Events in the interval 1989-1991; compare to \cite{Takahashi2010} Fig.~11. Bottom: Events in the interval 1983-1991.}
\label{DailyAveragedDstEvents}
\end{figure}

\begin{figure}[tp!]
\centering
\includegraphics[scale=0.40]{figures/stormavs-dst.eps}
\rule[1ex]{5cm}{1pt}
\includegraphics[scale=0.40]{figures/stormavs-dd12-GOES6.eps}
\caption{$D_{st}$ events from GOES 6 using hourly medians. Top: Events in the interval 1983-1991; compare to bottom panel {DailyAveragedDstEvents}. Bottom: Same as Top except for constraint that $D_{st}$ stayed below $-50$~nT for at least 12~hours after crossing below $-50$~nT.}
\label{HourlyAveragedDstEvents}
\end{figure}

@@

\begin{figure}[htp!]
\centering
\includegraphics[scale=0.40]{figures/stormavs-mass-gt20-GOES6.eps}
\caption{$\req\ > 20$~ amu/cm$^3$ events from GOES 6 using hourly medians. As described in the text, there is no statistically significant dependence of the \req\  plot on $B_z$ in the time interval of $\pm 2$~hours around the event.}
\label{HourlyAveragedRhoEvents}
\end{figure}

\begin{figure}[tp!]
	\centering
	\includegraphics[scale=0.40]{figures/RhoBinnedBz-case24-t020-tf25-GOES6.eps}
	\includegraphics[scale=0.40]{figures/RhoBinnedBz-case24-t025-tf30-GOES6.eps}
	\caption{Binning \req\ events by $B_z$ value (a) at onset and four hours before, and (b) at onset and four hours after.}
	\label{fig:RhoBinned}
\end{figure}
